\documentclass{article}
\usepackage{array,longtable, pagecolor, xcolor}
\usepackage{lipsum}
\usepackage{fourier}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\usepackage[bottom=1cm, left=0cm, right=4cm, top=1.3cm]{geometry}
\pagenumbering{gobble}
\pagecolor{white}

\makeatletter
\newcommand{\globalcolor}[1]{%
  \color{#1}\global\let\default@color\current@color
}
\makeatother

\AtBeginDocument{\globalcolor{black}}


\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Kareem's resume},
    bookmarks=true,
    pdfpagemode=FullScreen,
}

\begin{document}

    \begin{changemargin}{2cm}{-2cm}
        \begin{center}
        {\Huge Kareem Arab}\par\smallskip\smallskip

        \begin{minipage}[b]{0.33333\textwidth}
        \centering
            me@kareemarab.com  \par
            % 613.255.5483 --- Ottawa, Canada\par
            Ottawa, Canada\par
            \textbf{\href{http://kareemarab.com}{kareemarab.com}}
        \end{minipage}
        \end{center}
    \end{changemargin}

    \begin{longtable}{@{}>{\raggedleft}p{0.25\linewidth}
                          p{\dimexpr0.75\linewidth-2\tabcolsep-\arrayrulewidth\relax}>{}p{0.25\linewidth}@{}}

        \textbf{languages,}
            & \textbf{\textsc{Swift --- Java --- Python --- TypeScript --- SQL --- HTML/(S)CSSß}} \\
        \textbf{frameworks and technologies}
            & \textbf{\textsc{iOS, iPadOS, XCode, Realm, Serverless (AWS Lambda/GCP Functions) --- GCP --- AWS --- K8s --- Helm --- Docker --- Vault --- CI/CD (XCode Cloud, Github Actions, Jenkins, Spinnaker) --- TensorFlow --- SpringBoot --- MySQL --- Redis --- DynamoDB --- Ionic --- Firebase --- Rancher --- Splunk --- Latex}}\\ [5em]

        \textbf{work experience}
            & \textbf{\textsc{\href{https:/https://amadeus.com/en}{Amadeus}}} & \textit{Mar 2021 - present}\\
            & \textit{Full Stack Engineer} \\
            & - Developed and integrated \textbf{Multi-Factor Authentication (MFA)} into our existing authentication service, enhancing account security for millions of users. \\
            & - Developed and executed multiple service deployments to Rancher K8s and caching, resulting in self-healing deployments, increased capacity and reduced database load. \\
            & - Responsibility over system components \& onboarding of new engineers. \\
		    & - Designed and developed internal tools (user-management, code-review listing, etc.) that help developers in their development process. \\ [2em]

            & \textbf{\textsc{\href{https://www.neurovine.ai/}{Neurovine}}} & \textit{Apr 2019 - Feb 2021}\\
            & \textit{Software Engineer} \\
            & - Shipped \textbf{APIs} built on \textbf{AWS Lambda} (serverless) that drove our mobile and research portal apps. It also drove our internal data-science pipeline. \\
		    & - Developed a consumer mobile app \& research portal using \textbf{Ionic}. \\
		    & - Collaborated w/ Data Science team to build a \textbf{Python} \textbf{real-time} EEG analysis system. \\
		    & - Helped implement \textbf{HIPPA} requirements across our systems. \\ [1em]

        \textbf{education}
            & \textbf{\textsc{Carleton University}} & \textit{Spring 2020} \\
            & Bachelor of Computer Science (BSc) \\ [1em]

        \textbf{projects}
            & \textbf{\textsc{Handshake} -- iOS App } & \textit{2018} \\
            & - Private real-time group chat w/ built-in event management - beta. Built using \textbf{Swift}, \textbf{Firebase}, \textbf{Google Cloud Functions}, \textbf{Cloud Scheduler}  and \textbf{Realm DB}.\\ [2em]

            & \textbf{\textsc{\href{https://github.com/kareemarab/trnd}{\textbf{Trnd}}}} & \textit{2018} \\
            & - A social network app for GIFs. Built using \textbf{Swift} and \textbf{Parse}. \\ [1em]

            & \textbf{\textsc{\href{https://github.com/kareemarab/advatck}{\textbf{Guassian/Carlini-Wagner Adversarial Attacks}}}}\ & \textit{Winter 2020} \\
            & - Comparing the effects of Gaussian and Adversarial Perturbations on a convolutional neural network's input space. \\ [2em]

            & \textbf{\textsc{\href{https://github.com/kareemarab/neuralnets}{\textbf{Neural Networks}}}} & \textit{Summer 2020} \\
            & - A collection of different Implementations of neural networks (Hopfield, RBF and Convolutional) built using \textbf{TensorFlow}. \\ [2em]

            % & \textbf{\textsc{\href{https://github.com/kareemarab/glance}{\textbf{Glance}}}} & \textit{2018} \\
            % & - \textbf{Linux OS} Task Manager written in Python \\ [1em]

            & ** More \textbf{projects} on \textit{\href{https://github.com/kareemarab}{\textbf{github}}}.\\ [1em]

        \textbf{achievements}
            & \textbf{\textsc{Shopify --- Build Things App Award}} & \textit{Nov 2018} \\
            & \textit{Winner of the best App award @ Shopify's Build Things App Showcase}. \\ [1em]

        \textbf{research}
            & \textbf{\textsc{IoT Lab @ Carleton University}} & \textit{2017 - 2019} \\
            & \textit{Undergraduate Researcher} \\
            & - Researched the best performing inference techniques on Smart Grid energy data. \\
            & - Built real-time multi-modal data streaming system using a Raspberry-pi and IBM Cloud. \\ [2em]
            % & - Learned to work w/ \textbf{Neural Networks} and \textbf{Wireless Sensor Communications} \\ [1em]

            & \textbf{\textsc{Diabetes Coach (Macadamian---IoT Lab)}} & \textit{Winter 2018} \\
            % & \textit{Research \& Development Intern}\\
            & - Helped build a system that aims to improve the lives of type II diabetes patients through self-management using voice control and real-time feedback. \\ [2em]

        \textbf{publications}
            % & \textbf{\textsc{AI for Diabetes Mellitus Type II: Forecasting and Anomaly Detection}} & \textit{2019}\\
            % & \textit{Author --- IEEE Wireless Communications and Networking Conference}  \\ [1em]
            % & \textbf{\textsc{Data Communication and Analytics for Smart Grid Systems}} & \textit{2018}\\
            % & \textit{Co-author --- IEEE International Conference on Communications}\\ [1em]
            & ** All \textbf{publications} on \textit{\href{https://scholar.google.ca/citations?user=zFDREhgAAAAJ\&hl=en}{\textbf{google scholar}}}.\\ [1em]

  \end{longtable}

\end{document}